Detecting Stylistic Variation in Pop Production

### 2023-12-01 outputs/paper/paper.qmd
abstract lol

---
title: "Detecting Stylistic Variation in Pop Production"
author: 
  - name: Michaela Drouillard
thanks: "Code and data are available at: https://github.com/michaeladrouillard/spotify_pop. We thank Rohan Alexander, Carl Wilson and Inessa De Angelis for valuable suggestions. For any comments or suggestions, please contact michaela.drouillard@mail.utoronto.ca"
date: "today"
date-format: "long"
abstract: "This study investigates the feasibility of predicting whether a song is produced by Jack Antonoff using Spotify's audio feature API. We developed two models: a logistic regression model and a random forest model. The logistic regression model, focusing on Antonoff's collaborators' discographies, demonstrates an accuracy of 76%, precision of 39%, and a recall of 76% when predicting whether a track has an Antonoff credit. The random forest model, which includes discographies of other notable pop producers, shows an accuracy of 61% when predicting tracks' producers, comparing favorably to a No Information Rate of 43%. A significant finding is that 'danceability', a metric developed from human-tagged data, emerges as a crucial predictor in both models. This research contributes to the broader understanding of computational analysis in cultural contexts, illustrating how a blend of human judgment and algorithmic processing can approximate musical styles"
format: pdf
number-sections: true
bibliography: references.bib
csl: modern-language-association.csl
number-depth: 2
---

>>>>

---
title: "Detecting Stylistic Variation in Pop Production"
author: 
  - name: Michaela Drouillard
thanks: "Code and data are available at: https://github.com/michaeladrouillard/spotify_pop. We thank Rohan Alexander, Carl Wilson and Inessa De Angelis for valuable suggestions. For any comments or suggestions, please contact michaela.drouillard@mail.utoronto.ca"
date: "today"
date-format: "long"
abstract: "This study investigates the feasibility of predicting whether a song is produced by Jack Antonoff using Spotify's audio feature API. We developed two models: a logistic regression model and a random forest model. The logistic regression model, focusing on Antonoff's collaborators' discographies, demonstrates an accuracy of 76%, precision of 39%, and a recall of 76% when predicting whether a track has an Antonoff credit. The random forest model, which includes discographies of other notable pop producers, shows an accuracy of 61% when predicting tracks' producers, comparing favorably to a No Information Rate of 43%. A significant finding is that 'danceability', a metric developed from human-tagged data, emerges as a crucial predictor in both models. This research contributes to the broader understanding of computational analysis in cultural contexts, illustrating how a blend of human judgment and algorithmic processing can approximate musical styles."
format: pdf
number-sections: true
bibliography: references.bib
csl: modern-language-association.csl
number-depth: 2
---
